---
title: Coursera assignment - vignette for FARS (Fatality Analysis Reporting System)
  functions
author: "Kévin Allan Sales Rodrigues"
date: '2020-06-28'
output:
  html_document: default
  pdf_document: default
vignette: |
  %\VignetteIndexEntry{Coursera assignment - vignette for FARS (Fatality Analysis Reporting System) functions} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---


## General Features of This Package

The `RpackageCoursera` aims to analyze data on incidents from NHTSA (National Highway Traffic Safety Administration) (link to data https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars). This package contains a total of 5 functions: `fars_map_state`, `fars_read`, `fars_read_years`, `fars_summarize_years` and `make_filename`. At the time of reading the data, it is assumed that the files are in the NHTSA standard format.

Next, this document shows how to use the 5 functions.

## Function Descriptions

### fars_map_state

The fars_map_state function receives the number and year of the state as input and creates a graph with the location of the fatal injuries for the selected state and year.

> Correct way to use the `fars_map_state` function
```{r eval=FALSE}
fars_map_state(2, 2013)
```

> Incorrect ways to use the `fars_map_state` function
```{r eval=FALSE}
fars_map_state("2013, 2")
fars_map_state("2, 2013")
fars_map_state("2", 2013)
fars_map_state("2", "2013")
fars_map_state(2, "2013")
```

### fars_read

The `fars_read` function reads the FARS data and returns a dataframe.

> Correct way to use the `fars_read` function
```{r eval=FALSE}
fars_read("data.csv") # where "data.csv" is the FARS data archive
```

### fars_read_years

The `fars_read_years` function is an auxiliary function used by fars_summarize_years that reads FARS data stored as csv for the provided input years (taken as list or vector) and returns a list, for each year the corresponding element of the list will be a tibble with number of rows equal to the number of observations and two columns: MONTH and year.

> Correct way to use the `fars_read_years` function
```{r eval=FALSE}
fars_read_years(c(2014, 2015))
```

> Incorrect ways to use the `fars_read_years` function
```{r eval=FALSE}
fars_read_years(c("2014, 2015"))
fars_read_years(c("2014", 2015))
fars_read_years(c(2014, "2015"))
```


### fars_summarize_years

The `fars_summarize_years` function receives a list of as input, reads the respective data from the working directory and returns a summary table that contains the number of accidents grouped by year and month from the specified list of years.

> Correct way to use the `fars_summarize_years` function
```{r eval=FALSE}
fars_summarize_years(c(2014, 2015))
```

> Incorrect ways to use the `fars_summarize_years` function
```{r eval=FALSE}
fars_summarize_years(c("2014, 2015"))
fars_summarize_years(c("2014", 2015))
fars_summarize_years(c(2014, "2015"))
```

### make_filename

This function takes the year as either a string or an integer as input and returns the file name of the FARS data stored as csv and returns a file name from a table that contains a slide of data from the NHTSA FARS of desired year.


> Correct way to use the `make_filename` function
```{r eval=FALSE}
make_filename("2013")
```


<!-- end of file -->


